%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks, hyperfootnotes=false, pdfpagemode=UseNone]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{fontawesome5}
\usepackage{ragged2e}
\usepackage[none]{hyphenat}
\usepackage[sfdefault]{FiraSans}
% \setlength{\multicolsep}{-3.0pt}
\hypersetup{hidelinks}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\usepackage{xcolor}
\hypersetup{colorlinks,urlcolor=blue}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.4in}
\addtolength{\evensidemargin}{-0.4in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small \raggedright{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\achievementItem}[1]{
  \item\small{
    {#1 \vspace{-6pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-0pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\newResumeSubheading}[2]{
\vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2}
      % \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\justify \begin{itemize} \vspace{-1pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\hypersetup{pdfcreator={}, pdftoolbar=false, pdfmenubar=false}
\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Jai Kumar Dewani} \\ \vspace{1pt}
    % 123 Street Name, Town, State 12345 \\ 
\small 9340422023 \quad \textbullet \quad
\href{mailto:jai.dewani.99@gmail.com}{jai.dewani.99@gmail.com} \quad \textbullet \quad
\href{https://www.linkedin.com/in/jai-dewani/}{linkedin.com/in/jai-dewani} \quad \textbullet \quad
\href{https://github.com/jai-dewani}{github.com/jai-dewani}
        
    % \small \raisebox{-0.1\height}\faPhone\ 9340422023 ~ 
    % \raisebox{-0.2\height}\faEnvelope\ \href{mailto:jai.dewani.99@gmail.com}{ jai.dewani.99@gmail.com} ~ 
    % \raisebox{-0.2\height}\faLinkedin\ \href{https://www.linkedin.com/in/jai-dewani/}{ linkedin.com/in/jai-dewani}  ~
    % \raisebox{-0.2\height}\faGithub\ \href{https://github.com/jai-dewani}{ github.com/jai-dewani}
    % \vspace{-8pt}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\newResumeSubheading
    {Carl Zeiss - Vision Care R\&D and Technologies}{Bengaluru, Karnataka, India}
    % {Senior Software Design Engineer \quad | \quad Software Design Engineer \quad | \quad Software Engineer}{June 2021 -- Present}
    \vspace{-14pt}
    % Senior Software Design Engineer
    \resumeSubSubheading{Senior Software Design Engineer}{Jan 2025 -- Present}
    \resumeItemListStart
        \resumeItem{Leading Refraction Unit architecture and feature roadmap, ensuring scalable long-term platform design.}
        \resumeItem{Driving product–engineering alignment to deliver next-generation optometry solutions.}
        \resumeItem{Authored medical-system integration documentation to streamline release processes and reduce cross-team ambiguity.}
    \resumeItemListEnd

    % Software Design Engineer
    \resumeSubSubheading{Software Design Engineer}{July 2022 -- Dec 2024}
    \resumeItemListStart
        \resumeItem{Led VISUCORE R1.1 delivery, coordinating cross-team technical decisions and workflows.}
        \resumeItem{Owned migration of 15+ legacy .NET Framework 4.8 modules to .NET 8, reducing startup time by 22\% and improving security posture.}
        \resumeItem{Built an event-queue command-coalescing system to merge high-frequency user interactions, cutting hardware execution time by 90\% and improving UX.}
        \resumeItem{Built a C++ interop wrapper that stabilized hardware communication and reduced integration effort by 30\%.}
        \resumeItem{Contributed to hiring processes for both early-career and experienced engineers, strengthening overall engineering capability.}
    \resumeItemListEnd

    % Software Engineer
    \resumeSubSubheading{Software Engineer}{June 2021 -- June 2022}
    \resumeItemListStart
        \resumeItem{Improved engineering velocity by upgrading mocking infrastructure, cutting test runtime by 80\% and reducing reliance on 3rd-party services.}
        \resumeItem{Drove alignment across software, hardware, and product teams to establish clean, extensible API contracts.}
        \resumeItem{Integrated gRPC for IPC between services, reducing coupling and enabling parallel development across modules.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {International Institute of Information Technology, Naya Raipur}{August 2017 -- June 2021}
      {Bachelor of Technology in Computer Science}{Naya Raipur, Chhattisgarh India}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \newResumeSubheading
            {\textbf{Password Manager System} $|$ \emph{C\#}}{Mar 2025 - Sep 2025}
            \resumeItemListStart
                \resumeItem{Extended Password Manager compatibility to VC500-connected VTS devices, enabling secure credential handling across the ecosystem.}
                \resumeItem{Owned requirement clarification, solution design, and implementation across teams.}
                \resumeItem{Engineered a robust restart notification framework, improving system observability and reliability.}
            \resumeItemListEnd
        \resumeProjectHeading
            {\textbf{Subjective Refraction Platform} $|$ \emph{C\#, Angular}  $|$ \href{https://www.zeiss.com/vision-care/int/eye-care-professionals/equipment/refraction/combined-refraction-unit.html}{VISUCORE Product Page}}{Jan 2021 - Current}
            \resumeItemListStart
                \resumeItem{Owned the development of visual acuity testing module for market releases - R1 and R1.1}
                \resumeItem{Orchestrated the design of an asynchronous Refraction module, improving workflow performance by 28\%.}
                \resumeItem{Implemented lock-and-release mutual-exclusion mechanism, improving system stability.}
                \resumeItem{Introduced atomic command execution guarantees, simplifying concurrent workflows and reducing developer cognitive load.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    {\item{
     \textbf{Languages}{: C\#, Python, JavaScript, TypeScript } \\
     \vspace{1pt}
     \textbf{Frameworks}{: .NET 8, .NET Framework, ASP.NET, WPF, NUnit, Node.js, gRPC, Angular, React} \\
     \vspace{1pt}
     \textbf{Developer Tools}{: Azure, MSBuild, MySQL, SonarQube, Blackduck, IRIUS Risk, Docker, GitHub Actions, CI/CD} \\
    }}
 \end{itemize}
 \vspace{-16pt}



%-----------INVOLVEMENT---------------
\section{Achievements}
\begin{itemize}[leftmargin=0.2in]
  \achievementItem{Recognized with the \textbf{Ownership Spirit} award (2025 Zeiss offsite) for leading resolution of high-impact system-blocking customer issues.}
  \achievementItem{Speaker at FOSS Conference on how Zeiss leverages and contributes to open-source frameworks.}
  \achievementItem{Contributed to open-source projects including Excalidraw and Microsoft PowerToys.}
  \achievementItem{Mentored and judged 100+ teams at national hackathons including HackCBS, HackOn, and DotSlash.}
  \achievementItem{Qualified \textbf{ACM ICPC Regionals} (Top 100 Nationwide across 2019–2020).}
\end{itemize}


\end{document}
\phantom{}